Division and Factorization of p-Adic Polynomials

### 2016-01-29 polynomials/muldivfact.tex
Change comments on (X+1)^5+2

The modulus $(X+1)^5 + 2$ shows the advantage of working
with lattice precision in intermediate computations.  While
a small amount of the precision gain is diffuse, the number of
diffuse $p$-adic digits remains constant as $n$ increases,
and the increase in precision on the actual coefficients
increases almost on pace with $X^5 + 2$.  In contrast,
non-lattice methods for $(X+1)^5 + 2$ are on par
with the other non-Eisenstein examples.

@@

The rest of this subsection is devoted to the proof of the theorem.
If $d = n$ (resp. $d = 0$), the sequence $A_i$ is constant equal to
$P$ (resp. to the constant coefficient of $P$) and theorem is clear. \todo{Should this be $d=0$? (Tristan:) I agree, I have tried to change accordingly the previous and following statement.}
We then assume $1 \leq d < n$. Without loss of generality, we may further 
assume that the coefficient $a_d$ is equal to $1$. We set:
\begin{align*}
\lambda_0 & = \NF(P)(d) - \NF(P)(d{-}1) \\
\lambda_1 & = \NF(P)(d{+}1) - \NF(P)(d),
\end{align*}
so that $\kappa = \lambda_1 - \lambda_0$.
The existence of an extremal point of $\NP(P)$ located at abscissa
$d$ ensures that $\lambda_1 > \lambda_0$, \emph{i.e.} $\kappa > 0$.
For all indices $i$, we define:
$$\begin{array}{r@{\,\,}lr@{\,\,}l}
Q_i &= V_i P \div A_i, &
R_i & = V_i P \mod A_i = A_{i+1} - A_i, 
\smallskip \\
S_i &= P \mod A_i, &
T_i &= (1 - V_i B_i) \mod A_i
\end{array}$$
and when $\square$ is some letter, we put $\Delta \square_i = \square_{i+1} 
- \square_i$.
%We use the next Lemma to record some useful formulae.

>>>>

The modulus $(X+1)^5 + 2$ shows the advantage of working
with lattice precision in intermediate computations.  Indeed,
the precision behavior using the lattice model closely parallels
that of $X^5+2$, since the lattices are related by a change of
variables.  But this structure is not detected in the Newton
or jagged models.

@@

The rest of this subsection is devoted to the proof of the theorem.
If $d = n$ (resp. $d = 0$), the sequence $A_i$ is constant equal to
$P$ (resp. to the constant coefficient of $P$) and theorem is clear.
We then assume $0 < d < n$. Without loss of generality, we may further 
assume that the coefficient $a_d$ is equal to $1$. We set:
\begin{align*}
\lambda_0 & = \NF(P)(d) - \NF(P)(d{-}1) \\
\lambda_1 & = \NF(P)(d{+}1) - \NF(P)(d),
\end{align*}
so that $\kappa = \lambda_1 - \lambda_0$.
The existence of an extremal point of $\NP(P)$ located at abscissa
$d$ ensures that $\lambda_1 > \lambda_0$, \emph{i.e.} $\kappa > 0$.
For all indices $i$, we define:
$$\begin{array}{r@{\,\,}lr@{\,\,}l}
Q_i &= V_i P \div A_i, &
R_i & = V_i P \mod A_i = A_{i+1} - A_i, 
\smallskip \\
S_i &= P \mod A_i, &
T_i &= (1 - V_i B_i) \mod A_i
\end{array}$$
and when $\square$ is some letter, we put $\Delta \square_i = \square_{i+1} 
- \square_i$.
%We use the next Lemma to record some useful formulae.
